---
title: "CS165B Assignment 2"
author: "Shaoyi Zhang"
date: "April 22, 2016"
output: pdf_document
---

## Problem 1.a
number of errors = 8+0+1+0+0+0+0+0 = 9
There are 9 ranking errors. 

## Problem 1.b
#### rank error rate = number of errors /(P*N) = 9 / (12 * (20 - 12)) = 0.09375

## Problem 1.c
#### rank accuracy = 1 - rank error rate = 1 - 0.09375 = 0.90625

## Problem 1.d
```{r}
library(ggplot2)
negative=c(0,0,0,0,0,0,1,1,2,3,3,4,5,6,7,8,8,9,10,11,12)
positive=c(0,1,2,3,4,5,5,6,6,6,7,7,7,7,7,8,8,8,8,8,8)
pt = data.frame(negative,positive)

p <- ggplot(pt, aes(negative, positive))+xlim(0,12)+ylim(0,8)
p + geom_point(size=3)
```

##Problem 2.a
```{r,echo=FALSE}


negative=c(0,0,1,3,6,10)
positive=c(0,4,11,13,15,15)
lab = data.frame(negative,positive)

p <- ggplot(lab, aes(negative, positive))+xlim(0,10)+ylim(0,15)
p + geom_point(size=3)
```



##Problem 3
```{r}
x1 = c(2,3,1,1,4,2,1,0,4,3,3)
x2 = c(2,3,2,4,4,2,1,4,0,3,3)
x3 = c(3,2,3,1,4,2,1,2,0,1,3)
label = c("+","+","+","+","+","+","-","-","-","-","-")
p3 = data.frame(x1,x2,x3,label)
p3$classifer = p3$x1 * 2 + p3$x2 +3 * p3$x3
p3$margin = (p3$classifer - 12)/sqrt(2^2 + 3^2 + 1)
p3$zeroOneLoss[p3$margin<=0] = 1
p3$zeroOneLoss[p3$margin>0] = 0
p3$hinge = p3$margin
p3$hinge[p3$margin>=1] = 0
p3$hinge[p3$margin<1] = 1-p3$margin[p3$margin<1]
p3$squareLoss = (p3$hinge)^2
p3$squareLoss[p3$margin>1] = 0
p3
```


## Problem 2.b
```{r,echo=FALSE}
negative=c(0,0,1,3,6,10)
positive=c(0,4,11,13,15,15)
negative = negative/15
positive = positive/15

roc = data.frame(negative,positive)
p <- ggplot(roc, aes(negative, positive))+xlim(0,1)+ylim(0,1)
p + geom_point(size=3)
```

## Problem 2.c
##### Accuracy 
 Hightest = C2,C3     Lowest = C0

## Problem 2.d
##### Average Recall
 Highest = C2     Lowest = C0,C5

## Problem 2.e
C4, C5  A concept is complete if it covers all positive example. 

## Problem 2.f
C0, C1 A concept is consistent if it covers none of the negative examples.

## Problem 4
```{r}
library(gridExtra)
index = c(1,2,3,4,5)
occurrence = c(2,4,8,0,11)
freq = occurrence/25
laplace = (occurrence+1)/(25+5)
m5 = (occurrence+5/5)/(25+5)
m20 = (occurrence+20/5)/(25+20)
p4 = data.frame(index,freq,laplace,m5,m20)
p4

p4plot1 = ggplot(p4,aes(index,freq))+xlim(1,5)+ylim(0,1)+ geom_point(size = 3)

p4plot2 = ggplot(p4,aes(index,laplace))+xlim(1,5)+ylim(0,1)+ geom_point(size = 3)

p4plot3 = ggplot(p4,aes(index,m5))+xlim(1,5)+ylim(0,1)+ geom_point(size = 3)

p4plot4 = ggplot(p4,aes(index,m20))+xlim(1,5)+ylim(0,1)+ geom_point(size = 3)

grid.arrange(p4plot1,p4plot2,p4plot3,p4plot4)
```

##### As we increase pesudocount the probability distribution is flatten.


## Problem 5.a
```{r}
T = 2^(4+2+3+4)
T
```
## Problem 5.b
```{r}  
T = 1*(4+1)*(2+1)*(3+1)*(4+1)
T
```
  
## Problem 5.c
```{r}
T = 1*(2^4-1)*(2^2-1)*(2^3-1)*(2^4-1)
T
```



